### 2018-07-12 doc/plos/text/manuscript.tex
start results section
Add some basic stats, a table, and make figures in-line with text.
Figures will be removed from the final version.

@@

@@

% Don't include figures in the final version. This is just for preview.
\newgeometry{top=1.0in,left=1.0in,footskip=30pt}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_top.png}
  Figure 1 (top).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_bottom.png}
  Figure 1 (bottom).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/all_nowcasts.png}
  Figure 2.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_sensors.png}
  Figure 3.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_ablation.png}
  Figure 4.
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/accuracy_vs_abscission.png}
  Figure 5.
\end{figure}

>>>>

% TODO: don't include graphics in the final version
\newcommand{\maybeincludegraphics}[1]{\includegraphics[width=\textwidth]{../data/figures/#1.png}}

@@

\subsection*{Sensors}

% python3 analyze.py sensor_info
% gft:
%   num national: 254
%   first week: 201040
%   last week: 201532
%   num locations: 62
% ght:
%   num national: 402
%   first week: 201040
%   last week: 201824
%   num locations: 52
% twtr:
%   num national: 339
%   first week: 201151
%   last week: 201824
%   num locations: 71
% wiki:
%   num national: 402
%   first week: 201040
%   last week: 201824
%   num locations: 1
% cdc:
%   num national: 276
%   first week: 201310
%   last week: 201824
%   num locations: 71
% epic:
%   num national: 119
%   first week: 201442
%   last week: 201819
%   num locations: 15
% sar3:
%   num national: 402
%   first week: 201040
%   last week: 201824
%   num locations: 75
% arch:
%   num national: 265
%   first week: 201040
%   last week: 201820
%   num locations: 20
% total num readings: 113164

In total, we obtained 113,164 individual sensor readings from the eight
surveillance sources discussed above. Table~\ref{table_sensor_breakdown} gives
a breakdown of the number of weeks and locations covered by each source.
Fig~\ref{figure_sensor_heatmap} shows time-series of sensor readings for the US
as a whole, which is the only location common to all data sources.

\begin{table}[!ht]
  \centering
  \caption{{\bf TODO(Table caption.)}}
  \begin{tabular}{|l|l|l|}
    \hline
    {\bf Source} & {\bf Weeks} & {\bf Locations}\\ \thickhline
    GFT & 254 & 62 \\ \hline
    GHT & 402 & 52 \\ \hline
    TWTR & 339 & 71 \\ \hline
    WIKI & 402 & 1 \\ \hline
    CDCP & 276 & 71 \\ \hline
    EPIC & 119 & 15 \\ \hline
    SAR3 & 402 & 75 \\ \hline
    ARCH & 265 & 20 \\ \hline
  \end{tabular}
  \begin{flushleft}
    TODO(Table notes.)
  \end{flushleft}
  \label{table_sensor_breakdown}
\end{table}

\begin{figure}[!h]
  \maybeincludegraphics{sensor_heatmap_top}
  \maybeincludegraphics{sensor_heatmap_bottom}
  \caption{
    {\bf TODO(figure title.)}
    TODO(Figure caption top and bottom.)
  }
  \label{figure_sensor_heatmap}
\end{figure}

\subsection*{Nowcasts}

% python3 analyze.py nowcast_info
% num national nowcasts: 397
% first week: 201045
% last week: 201824
% total num nowcasts: 29103
% num locations: 75

In total, we produced 29,103 nowcasts for 75 US locations across 397 weeks
spanning 2010w45--2018w24. Locations include the US as a whole, the 10 HHS
regions, the 9 census divisions, the 50 states, the District of Columbia,
Puerto Rico, the US Virgin Islands, New York City, and New York state
\textit{excluding} New York City. Although these were computed in retrospect,
models were trained using only data that would have been available at the time.
Namely, whenever possible, preliminary values of wILI were used in place of
final values.

@@
